Static contract checking for Haskell

### 2011-10-20 paper.tex
Paper: made a pass through section 2, with some section 1 fixes along the way.

% Margin notes round two (easier and better looking)
%
% http://trackchanges.sourceforge.net/help_stylefile.html
\usepackage[inline]{trackchanges} % [margins] is also good
\addeditor{nc}

@@

Then, we must state that $Nil$ never crashes (ie cannot be evaluated
to an exception) and that $Cons(x,y)$ \add[nc]{never} crashes iff \change[nc]{either}{both} $x$ \change[nc]{or}{and} $y$
\add[nc]{never} crash. The statement $x$ \add[nc]{never} crashes is encoded by the term $\cf{x}$\note[nc]{Made more precise in section \ref{sec:cf}}.

@@

Now we translate the $null$ function. Note that the symbols $true$ and
$false$ are the representation of the data constructors $True$ and
$False$ in Haskell, not the boolean values $\top$ and $\bot$ in our
logic.\note[nc]{XXX, TODO: use $True$ and $False$ in the
  text.  The lowercase $true$ and $false$ is an artifact of the implementation, i.e. Equinox accepts TPTP format, which doesn't allow bare uppercase function symbols.  Moreover, the lower case here is inconsistent with the rest of the presentation, e.g. $Cons$ and $Nil$ above.}
\begin{equation*}
\forall xs.~ xs=Nil \implies notnull(xs) = false
\end{equation*}\note[nc]{Here we might ask the same question as above: why not use the simpler definition
\[
\forall notnull(Nil) = false
\]? The answer is that this is an expansion of the $etrans{e} = K_i(\vec{x_i}) \to a = \etrans{e_i}$ part of the $\dtrans{}$ rule for functions defined by cases.  I.e., the scrutinee $Nil$ is, in general, an expression involving, but not necessarily equal to, the arguments to the function.  In this special case we could remove the implication, but not in general.  The $a = \etrans{e_i}$ part is missing above, but I guess that's because this text was not updated for the $\min$-translation.}

@@

  OK, and actually this might be easy: we simply interpret all
  recursive function symbols (the $fp$'s for recursive $f$'s) as
  \unr{}, and use the fact that forall $x$, $\unr{}~x = \unr$.  Now,
  an easy induction on contract translations (Figure \ref{ctrans})
  gives \[ \emptyset \vdash \ctrans{\unr \in c}
  \]
  for all contracts $c$, and we're done!  Well, this is really just
  the base case, where all contracts in $T$ are for otherwise
  undefined recursion symbols ($fp$'s), but the inductive case is just
  as easy: given a consistent $T$, which may include contracts for
  defined symbols, we can always extend it to a consistent $T'$ by
  adjoining constracts for undefined symbols.

@@

Now, assume that $xs$ satisfies
$\cf{xs}$ and $notnull(xs) = true$.  We can derive that $xs \neq \bad$
because we have $\cf{xs}$ and \annote[nc]{$\lnot \cf{\bad}$}{Obviously true, given the definition of $CF$, but it's worth noting that this plays a key part in the axiomitization of $CF$, which is ommited in this draft (so far ...)}. The constraint
$notnull(xs) = true$ doesn't directly imply that $xs = Cons(y,ys)$ for
some $y$ and $ys$. But $notnull$ is totally defined, because of
\eqref{unrnotnull}. This implies (by \eqref{defnotnull}) that there exist
$y$ and $ys$ such that $xs = Cons(y,ys)$. Recalling $\cf{xs}$, we can
now derive $\cf{y}$ and $\cf{ys}$ (by \eqref{cfcons}). But $head(xs) =
y$ because of \eqref{defhead}, and $y$ is crash-free, so we can finally
derive $\cf{head(xs)}$. QED.

@@

The syntax of $\mathcal{H}$ is defined in figure~\ref{hprime-stx}. A module
is a list of toplevel definitions, claims that functions statisfy
contracts and data definitions.

\begin{itemize}
\item There's no $\lambda$-abstraction, because we can always lift
  them to toplevel declaration.
\item We do not allow nested case expressions, because once again, we
  can always lift them to the toplevel.
\item Until section~\ref{ho} we will only consider full application of
  functions ($f(x,y)$), in order to remove clutter. Dealing with
  partial application is not hard but a bit cumbersome.
\end{itemize}

@@

\subsection{Contracts}
Contract syntax is described in figure \ref{cont-stx}. The predicates
we use in our contracts can be any boolean $\hprime$ expression. We
only consider pairs of contract for simplicity, although there is no
issue with generalisation to arbitrary tuples.

@@

We give the semantics of contract by defining ``$e$ satisfies $t$'',
written $e \in t$ in figure \ref{cont-smt}. Note that this definition
doesn't yield any operative way to check that an expression actually
meets the specification given by its contract.

\begin{figure}[h]
 \centering
  \[  \begin{array}{rcl}
    e \in \{x \mid p \} &\iff& e \mbox{ diverges or } p[e/x] \not \to^\star \{\bad,False\}\\
    e \in x:c_1 \to c_2 &\iff& \forall e_1 \in c_1, (e~e_1) \in c_2[e_1/x]\\
    e \in (c_1,c_2) &\iff& e \mbox{ diverges or }\\
    &&  (e \to^\star (e_1,e_2) \mbox{ and } e_1 \in c_1, e_2 \in c_2)\\
    e \in c_1 \land c_2 &\iff& e \in c_1 \mbox{ and } e \in c_2 \\
    e \in c_1 \lor c_2 &\iff& e \in c_1 \mbox{ or } e \in c_2 \\
    e \in \cfc &\iff& e \mbox{ is crash-free}
  \end{array} \]
  \caption{Semantics of contract satisfaction}
  \label{cont-smt}
\end{figure}

\subsection{Crash-freeness}\label{sec:cf}
Note that $\cfc$ represents two things: it can be a contract, as in $f
\in \cfc$ or a special formula in first-order logic $\cf{f}$.

We use $\bad$ to signal that something has gone wrong in the program :
it has crashed.

\begin{definition}[Crash]
A closed term $e$ crashed iff $e \to^* \bad$.
\end{definition}

\begin{definition}[Diverges]
A closed expression $e$ diverges iff either $e \to^* \unr$ or there is
no value $val$ such that $e \to^* val$
\end{definition}

\begin{definition}[Syntactic safety]
A (possibly open) expression $e$ is syntactically safe iff $\bad \not
\in_s e$. Similarly a context \cal C is syntactically safe iff $\bad
\not \in_s \mathcal{C}$.
\end{definition}

The notation $\bad \not \in e$ means that $\bad$ does not appear
anywhere in $e$, similarly for $\bad \not \in_s \mathcal{C}$. For
example, $Just 3$ is syntactically safe whereas $Just \bad$ is not.

\begin{definition}[Crash-free]
An expression $e$ is said to be crash-free iff 
$$\forall \mathcal{C}.~\bad \not \in_s \mathcal{C} \mbox{ and } \vdash
\mathcal{C} \llbracket e \rrbracket :: () \mathcal{C} \not \to^* \bad$$
\end{definition}
The notation $\mathcal{C} \llbracket e \rrbracket :: ()$ means that
$\mathcal{C} \llbracket e \rrbracket$ is closed and well-typed.  Note
that there are crash-free expression that are not syntactically safe,
for example $fst~(1,\bad)$.

@@

One thing to notice is that $a$ and $b$ are things that ``sould not
happen'' but are caught statically whereas $c$ should not happen but
can only be dealt with dynamically.

We can now define two types of problematic expressions: those that
cannot happen during a run of the program and those that can.
Expressions of the first type are called unreachable (and equated to
the special value $\unr$ in our first-order theory), whilst
expressions of the latter type are called bad (and equated to the
special value $\bad$).

We said earlier that we only considered syntactically correct and
well-typed programs as input. That implies that the ``$a$'' case
cannot happen. But given that our first-order logic is not typed, the
theorem prover may decide to instanciate a variable with an ill-typed
value! In order to prevent this, we will need to encode some basic
type-checking mecanism directly in our first-order theory.

\subsection{First-order logic with equality}
We use first-order logic with equality, defined in figure \ref{fol-stx}.

\begin{figure}
 \centering
  \[  \begin{array}{rcl}
    v,w,s,t &:=& x \mid K(t,\dots,t) \mid f(t,\dots,t) \mid app(t,t)\\
    && \mid \bad \mid \unr \\
    \phi &:=& \forall x.\phi \mid \lnot \phi \mid \phi \lor \phi \mid \top \mid \bot \mid t=t \mid \mbox{CF}(t)\\
    && \mid \phi \land \phi \mid \phi \to \phi \mid \phi \tot \phi \\
    \Phi &:=& \epsilon \mid \phi \mid \Phi \cup \Phi \\
  \end{array} \]
  \caption{First-order logic syntax}
  \label{fol-stx}
\end{figure}

@@

\begin{figure*}
\[
\begin{array}{rcl}
  \multicolumn{3}{c}{\ruleform{\dtrans{def} = \Phi}} \\[2.5mm]
  \dtrans{\mbox{data } T = K_1, \dots, K_n} &=& \ktrans{\mbox{data } T = K_1, \dots, K_n} \\
  \dtrans{f \in c} &=& \ctrans{f \in c}\\
  \dtrans{f(\vec{x}) = e} &=& \forall \vec{x},a.~ (\min{a} \land a =
  f(\vec{x})) \to a = \etrans{e} \\
   \raisebox{ 0.5 cm }{$\dtrans{f(\vec{x}) = \mbox{case } e \mbox{ of } [K_i(\vec{x_i}) = e_i]}$} &\raisebox{0.5cm}{=}&  \hspace{-0.18cm} \begin{array}{rclcl}
     \forall \vec{x},a.~(\mbox{min}(a) \land a = f(\vec{x})) &\to&
     \multicolumn{3}{c}{  \texttt{min}(e) \land (e = \texttt{BAD} \lor
       \left(\bigvee_i \exists \vec{x_i}.~e = K_i(\vec{x_i})\right) \lor a = \texttt{UNR})} \\
     &\land& \forall \vec{x_1}.~\etrans{e} = K_1(\vec{x_1}) &\to& a = \etrans{e_1} \\
     &\land& & \cdots & \\
     &\land& \forall \vec{x_n}.~\etrans{e} = K_n(\vec{x_n}) &\to& a = \etrans{e_n}} \\
   \end{array} 
\end{array}
\]
\caption{$\dtrans{}$ -- Defintions translation}
 \label{dtrans}
 \note[nc]{??? Why do we introduce the extra quantified variable $a$,
   representing the result (``answer''?), instead of just using the result directly
   (which is logically equivalent)? Same question for the next
   Figure.  Does this make a difference to Equinox?}
\end{figure*}

@@

>>>>

% Margin notes round two (easier and better looking)
%
% http://trackchanges.sourceforge.net/help_stylefile.html
%
% NB: if you want to add a note in math mode, you need a trick:
%
% $ ... \text{\note{$<math note>$}} ... $
\usepackage[inline]{trackchanges} % [margins] is also good
\addeditor{nc}

@@

Then, we state that $Nil$ can cannot cause a crash, and that
$Cons(x,y)$ cannot cause a crash iff both its arguments cannot. The
statement ``$x$ cannot cause a crash'' is encoded by the formula
$\cf{x}$.\note[nc]{I just rewrote this, but it still sounds weird: in
  $head(Nil) = \bad$, who ``caused'' the crash? The precise definition
  of $\cf$ in Section \ref{sec:cf}, in terms of not leading to crashes
  when inserted into syntactically \bad-free environments,  is good, but
  how to state it informally?}

@@

Now we translate the $null$ function. Note that the symbols $true$ and
$false$ are the representation of the data constructors $True$ and
$False$ in Haskell, not the boolean values $\top$ and $\bot$ in our
logic.\note[nc]{XXX, TODO: use $True$ and $False$ in the
  text.  The lowercase $true$ and $false$ is an artifact of the implementation, i.e. Equinox accepts TPTP format, which doesn't allow bare uppercase function symbols.  Moreover, the lower case here is inconsistent with the rest of the presentation, e.g. $Cons$ and $Nil$ above.}
\begin{equation*}
\forall xs.~ xs=Nil \implies notnull(xs) = false
\end{equation*}\note[nc]{Here we might ask the same question as above: why not use the simpler definition
\[
notnull(Nil) = false
\]? The answer is that this is an expansion of the $etrans{e} = K_i(\vec{x_i}) \to a = \etrans{e_i}$ part of the $\dtrans{}$ rule for functions defined by cases.  I.e., the scrutinee $Nil$ is, in general, an expression involving, but not necessarily equal to, the arguments to the function.  In this special case we could remove the implication, but not in general.  The $a = \etrans{e_i}$ part is missing above, but I guess that's because this text was not updated for the $\min$-translation.}

@@

  OK, and actually this might be easy: we simply interpret all
  recursive function symbols (the $fp$'s for recursive $f$'s) as
  \unr{}, and use the fact that forall $x$, $\unr{}~x = \unr$.  Now,
  an easy induction on contract translations (Figure \ref{ctrans})
  gives \[ \emptyset \vdash \ctrans{\unr \in c} \]\note[nc]{

    Actually, this was not true!  We need an axiom saying $\cf{\unr}$.
    There was already such an axiom in the implementation, but it
    wasn't mentioned in this draft.  So, the correct statement is more
    like
    \[ \text{The Prelude} \vdash \ctrans{\unr \in c} \]

  } for all contracts $c$, and we're done!  Well, this is really just
  the base case, where all contracts in $T$ are for otherwise
  undefined recursion symbols ($fp$'s), but the inductive case is just
  as easy: given a consistent $T$, which may include contracts for
  defined symbols, we can always extend it to a consistent $T'$ by
  adjoining constracts for undefined symbols.

@@

Now, assume that $xs$ satisfies
$\cf{xs}$ and $notnull(xs) = true$.  We can derive that $xs \neq \bad$
because we have $\cf{xs}$ and \annote[nc]{$\lnot \cf{\bad}$}{

Follows from the definition of $CF$, but it's worth noting that this
plays a key part in the axiomitization of $CF$.

}. The constraint
$notnull(xs) = true$ doesn't directly imply that $xs = Cons(y,ys)$ for
some $y$ and $ys$. But $notnull$ is totally defined, because of
\eqref{unrnotnull}. This implies (by \eqref{defnotnull}) that there exist
$y$ and $ys$ such that $xs = Cons(y,ys)$. Recalling $\cf{xs}$, we can
now derive $\cf{y}$ and $\cf{ys}$ (by \eqref{cfcons}). But $head(xs) =
y$ because of \eqref{defhead}, and $y$ is crash-free, so we can finally
derive $\cf{head(xs)}$. QED.

@@

The syntax of $\mathcal{H}'$ is defined in figure~\ref{hprime-stx}. A module
is a list of toplevel definitions, claims that functions statisfy
contracts and data definitions.

\begin{itemize}
\item There's no $\lambda$-abstraction, because we can always lift
  them to toplevel declaration.
\item We do not allow nested case expressions, because once again, we
  can always lift them to the toplevel.
\item Until section~\ref{ho} we will only consider full application of
  functions ($f(x,y)$),\note[nc]{

Not really true: the definition of satisfaction for arrow contracts
$x:c_1 \to c_2$ already includes partial applications.  We could add a
special cases for each function arity, e.g.
\begin{eqnarray*}
&&\ctrans{f \in x_1:c_1 \to \cdots \to x_n:c_n \to c} \\
&&      :=\forall x_1, \ldots, x_n. \min{\etrans{f(x_1, \ldots, x_n)}} \\
&&\quad   \to \left( \bigvee_{i=1}^n \ctrans{x_i \notin c_i} \right)
              \lor \ctrans{f(x_1, \ldots, x_n) \in c}
\end{eqnarray*}
for functions of arity $n$, to make the claim true, but that would add
more clutter.  This may be related to my confusion where removing the
$f_{ptr}$ stuff caused problems where no higher-orderness was
involved?

}, in order to remove clutter. Dealing with
  partial application is not hard but a bit cumbersome.
\end{itemize}

@@

\subsection{Contracts}
Contract syntax is described in figure \ref{cont-stx}. The predicates
we use in our contracts can be any boolean $\hprime$ expression. We
only consider pairs of contract for simplicity, although there is no
issue with generalisation to arbitrary tuples.\note[nc]{

So, ``tuples'' refers to the the term constructor, not the type
constructor, and the generalization is e.g.
\[
e \in Cons(c_1,c_2) \iff e \text{ diverges or } 
      (e \to^\star Cons(e_1,e_2) \mbox{ and } e_1 \in c_1, e_2 \in c_2)
\]
?
}

@@

We give the semantics of contract by defining ``$e$ satisfies $c$'',
written $e \in c$ in the logic (figure \ref{cont-smt}), and 
\texttt{e ::: c} in code. Note that this definition
doesn't yield any operative way to check that an expression actually
meets the specification given by its contract.

\begin{figure}[h]
 \centering
  \[  \begin{array}{rcl}
    e \in \{x \mid p \} &\iff& e \mbox{ diverges or } p[e/x] \not \to^\star \{\bad,False\}\\
    e \in x:c_1 \to c_2 &\iff& \forall e_1 \in c_1, (e~e_1) \in c_2[e_1/x]\\
    e \in (c_1,c_2) &\iff& e \mbox{ diverges or }\\
    &&  (e \to^\star (e_1,e_2) \mbox{ and } e_1 \in c_1, e_2 \in c_2)\\
    e \in c_1 \land c_2 &\iff& e \in c_1 \mbox{ and } e \in c_2 \\
    e \in c_1 \lor c_2 &\iff& e \in c_1 \mbox{ or } e \in c_2 \\
    e \in \cfc &\iff& e \mbox{ is crash-free}
  \end{array} \]
   \caption{Semantics of contract satisfaction}

\note[nc]{

      ??? Does $\unr$ satisfy any contract? It's supposed to in the
      model sketched in the intro, and does intuitively, since we
      don't do termination analysis.  But now we can't prove the arrow
      case for $\unr$ in general, i.e.  $\ctrans{\unr \in x:c_1 \to
        c_2}$ is not provable for arbitrary $c_1$ and $c_2$ (I don't
      think).  Two solutions: (1) add the axiom $\forall x. \unr~x =
      \unr$ (the model uses this); (2) add the premise ``$e$ diverges
      or'' to the arrow case.

      Now, $\unr \in CF$ is intuitively true, for the Definition
      \ref{def:cf}, but to actually prove it it seems we need a
      semantics for evaluation that includes $\forall x. \unr~x =
      \unr$.  In the translation, $\ctrans{\unr \in CF}$ is provable,
      but only because of an axiom saying $\cf{\unr}$ :P

}
  \label{cont-smt}
\end{figure}

\subsection{Crash-freeness}\label{sec:cf}
Note that $\cfc$ represents two things: it can be a contract, as in $f
\in \cfc$ or a predicate in first-order logic, as in the formula $\cf{f}$.

We use $\bad$ to signal that something has gone wrong in the program :
it has crashed. (NB: looping is not crashing.)

\begin{definition}[Crash]
A closed term $e$ \emph{crashed} iff $e \to^* \bad$.\note[nc]{Again, the evaluation semantics are not given, but we assume that a pattern match failure is a crash.}
\end{definition}

\begin{definition}[Diverges]
A closed expression $e$ \emph{diverges} iff either $e \to^* \unr$ or there is
no value $val$ such that $e \to^* val$
\end{definition}

\begin{definition}[Syntactic safety]
A (possibly open) expression $e$ is \emph{syntactically safe} iff $\bad \not
\in_s e$. Similarly a context $\mathcal{C}$ is \emph{syntactically safe} iff $\bad
\not \in_s \mathcal{C}$.
\end{definition}

The notation $\bad \notin_s e$ means that $\bad$ does not appear
anywhere in $e$, similarly for $\bad \not \in_s \mathcal{C}$. For
example, $Just ~3$ is syntactically safe whereas $Just ~\bad$ is not.

\begin{definition}[Crash-free]\label{def:cf}
An expression $e$ is said to be \emph{crash-free} iff 
for all $\mathcal{C}$, $\bad \not \in_s \mathcal{C}$ and $\emptyset \vdash
\mathcal{C} \llbracket e \rrbracket :: ()$ implies $\mathcal{C} \llbracket e \rrbracket \not \to^* \bad$
\end{definition}
The notation $\emptyset \vdash \mathcal{C} \llbracket e \rrbracket :: ()$ means that
$\mathcal{C} \llbracket e \rrbracket$ is closed and well-typed.  Note
that there are crash-free expressions that are not syntactically safe,
for example $fst(Nil,\bad)$.

@@

One thing to notice is that $a$ and $b$ are things that ``should not
happen'' but are caught statically whereas $c$ should not happen but
can only be dealt with dynamically.\note[nc]{
I find this example confusing: \texttt{error} calls should be just as
easy to find as \texttt{undefined} calls statically.}

We can now define two types of problematic expressions: those that
cannot happen during a run of the program and those that can.
Expressions of the first type are called unreachable (and equated to
the special value $\unr$ in our first-order theory)\note[nc]{
%
In particular, ill-typed expressions are $\unr$, not $\bad$
%
}, whilst
expressions of the latter type are called bad (and equated to the
special value $\bad$).

We said earlier that we only considered syntactically correct and
well-typed programs as input. That implies that the ``$a$'' case
cannot happen. But given that our first-order logic is not typed, the
theorem prover may decide to instanciate a variable with an ill-typed
value! \change[nc]{In order to prevent this, we will need to encode some basic
type-checking mecanism directly in our first-order theory.}{This is OK, because the axioms are designed so that scrutinizing an ill-typed constructor-head results in $\unr$.  On the other hand, some ill-typed expressions are not $\unr$, e.g. we can prove that $tail(Cons(Nil,Z)) = Z$.}

\subsection{First-order logic with equality}
We use first-order logic with equality, defined in figure \ref{fol-stx}.\note[nc]{I guess ``with equality'' means that the proof theory has an axiom schema for substition, i.e. forall $phi$, $\forall x,y.x=y \to phi \iff phi[y/x]$, axioms making $=$ an equality relation, and the requirement that all models interpret $=$ as true equality on the carrier.}

\begin{figure}
 \centering
  \[  \begin{array}{rcl}
    v,w,s,t &:=& x \mid K(t,\dots,t) \mid f(t,\dots,t) \mid app(t,t)\\
    && \mid \bad \mid \unr \\
    \phi &:=& \forall x.\phi \mid \text{\add[nc]{$\exists x.\phi \mid$}} \lnot \phi \mid \phi \lor \phi \mid \top \mid \bot \mid t=t \mid \mbox{CF}(t)\\
    && \mid \phi \land \phi \mid \phi \to \phi \mid \phi \tot \phi \\
    \Phi &:=& \epsilon \mid \phi \mid \Phi \cup \Phi \\
  \end{array} \]
  \caption{First-order logic syntax}
  \note[nc]{The $\Phi$ are unnecessary and don't make things simpler, because a set of formulas is equivalent to the conjunction of its contents.  XXX, TODO: drop $\Phi$ and replace all $\bigcup$ with $\bigwedge$.}
  \label{fol-stx}
\end{figure}

@@

\begin{figure*}
\[
\begin{array}{rcl}
  \multicolumn{3}{c}{\ruleform{\dtrans{def} = \Phi}} \\[2.5mm]
  \dtrans{\mbox{data } T = K_1, \dots, K_n} &=& \ktrans{\mbox{data } T = K_1, \dots, K_n} \\
  \dtrans{f \in c} &=& \ctrans{f \in c}\\
  \dtrans{f(\vec{x}) = e} &=& \forall \vec{x},a.~ (\min{a} \land a =
  f(\vec{x})) \to a = \etrans{e} \\
   \raisebox{ 0.5 cm }{$\dtrans{f(\vec{x}) = \mbox{case } e \mbox{ of } [K_i(\vec{x_i}) = e_i]}$} &\raisebox{0.5cm}{=}&  \hspace{-0.18cm} \begin{array}{rclcl}
     \forall \vec{x},a.~(\mbox{min}(a) \land a = f(\vec{x})) &\to&
     \multicolumn{3}{c}{  \texttt{min}(e) \land (e = \texttt{BAD} \lor
       \left(\bigvee_i \exists \vec{x_i}.~e = K_i(\vec{x_i})\right) \lor a = \texttt{UNR})} \\
     &\land& \forall \vec{x_1}.~\etrans{e} = K_1(\vec{x_1}) &\to& a = \etrans{e_1} \\
     &\land& & \cdots & \\
     &\land& \forall \vec{x_n}.~\etrans{e} = K_n(\vec{x_n}) &\to& a = \etrans{e_n} \\%removed } here ...
   \end{array} 
\end{array}
\]
\caption{$\dtrans{}$ -- Defintions translation}
 \label{dtrans}
 \note[nc]{??? Why do we introduce the extra quantified variable $a$,
   representing the result (``answer''?), instead of just using the result directly
   (which is logically equivalent)? Same question for the next
   Figure.  Does this make a difference to Equinox?}
\end{figure*}

@@

\add[nc]{We also state that $\unr$ is crash-free: $\cf{\unr}$.}\note[nc]{

This is already present in the implementation, and assumed in the
consistency proof.}
